FireSim2019_ManuscriptFigures

### 2023-02-06 Manuscript-figures.Rmd
Include README file and finalize corncob scripts

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(out.width = '100%')
```

@@

df.fast <- subset(df.full, Experiment == 'fast growth' &
                        Estimate > (mean(Estimate)-1*sd(Estimate))) %>%
  mutate(fast.est = Estimate)%>%
  dplyr::group_by(OTU) %>%
  dplyr::mutate(max.Estimate = max(Estimate)) %>%
  subset(Estimate == max.Estimate) %>%
  subset(select = c(OTU, Estimate, SE, t, p, p_fdr,Comparison, Experiment,
                    horizon, Domain, Phylum, Class, Order, Family, Genus, 
                    Species, DNA.type, fast.est)) %>%
  unique()

@@

df.SI.responders <- df.full.OTU %>%
  subset(Experiment == 'fast growth') %>%
  merge(RDP)

@@

# Figure 6: Trade offs
```{r}
df <- read.csv('../data/sequence-data/LibCombined/corncob-output/all-responders.csv')
df.L2FC <- read.csv('../data/sequence-data/LibCombined/corncob-output/Full_L2FC.csv')

# Checking to make sure that L2FC calculations didn't drop any OTUs. 
df.survival <- df %>%
  subset(Experiment == 'survival'&
           Temp.cutoff %in% c('Low thermo greater than 50 C','Mid thermo greater than 50 C') & 
           Estimate > 0) %>%
  subset(Estimate > (mean(Estimate)-1*sd(Estimate)) ) %>% 
  subset(select = c(OTU,Phylum, Class, Order, Family, Genus, Species)) %>%
  unique()

df.survival.L2FC <- df.L2FC %>%
  subset(Experiment == 'survival'  &
           Temp.cutoff %in% c('low thermo greater than 50 C','mid thermo greater than 50 C') &
           mu > 0) %>%
  subset(mu > (mean(mu)-1*sd(mu))) %>%
  subset(select = c(OTU)) %>%
  unique()

@@

df.fast <- df %>%
  subset(Experiment == 'fast growth'&
           Estimate > 0) %>%
  subset(Estimate > (mean(Estimate)-1*sd(Estimate)) ) %>% 
  subset(select = c(OTU,Phylum, Class, Order, Family, Genus, Species)) %>%
  unique()
dim(df.fast)

df.fast.L2FC  <- df.L2FC %>%
  subset(Experiment == 'fast growth'  &
           mu > 0) %>%
  subset(mu > (mean(mu)-1*sd(mu))) %>%
  subset(select = c(OTU)) %>%
  unique() 
dim(df.fast.L2FC)
df.fast.merge <- merge(df.fast.L2FC, df.fast)

df.affinity <- df %>%
  subset(Experiment == 'affinity'&
           Temp.cutoff %in% c('Low thermo greater than 50 C','Mid thermo greater than 50 C') &
           Estimate > 0) %>%
  subset(Estimate > (mean(Estimate)-1*sd(Estimate)) ) %>% 
  subset(select = c(OTU,Phylum, Class, Order, Family, Genus, Species)) %>%
  unique()
dim(df.affinity)

df.affinity.L2FC  <- df.L2FC %>%
  subset(Experiment == 'affinity'  &
           Temp.cutoff %in% c('low thermo greater than 50 C','mid thermo greater than 50 C') &
           mu > 0) %>%
  subset(mu > (mean(mu)-1*sd(mu))) %>%
  subset(select = c(OTU)) %>%
  unique() 
dim(df.affinity.L2FC)

@@

# Create a dataframe for survivors filtering by temperature cutof and 1 sd from 
#   the mean of the estimate. Remove duplicate taxa. 
df.survival <- subset(df, Experiment == 'survival' &
                        Temp.cutoff %in% c('low thermo greater than 50 C','mid thermo greater than 50 C')) %>%
  subset(mu > (mean(mu)-1*sd(mu))) %>%
  mutate(survival.L2FC = L2FC) %>%
  dplyr::group_by(OTU) %>%
  dplyr::mutate(max.mu = max(mu)) %>%
  subset(mu == max.mu) %>%
  subset(select = c(OTU, survival.L2FC)) %>%
  unique()%>%
  mutate(survivor = 'yes')

# Create dataframe for fast growers filtering for 1 sd from the mean: -----
df.fast <- subset(df, Experiment == 'fast growth') %>%
  subset(mu > (mean(mu)-1*sd(mu))) %>%
  mutate(fast.L2FC = L2FC)%>%
  dplyr::group_by(OTU) %>%
  dplyr::mutate(max.mu = max(mu)) %>%
  subset(mu == max.mu) %>%
  subset(select = c(OTU, fast.L2FC)) %>%
  unique() %>%
  mutate(fast = 'yes')

# Create data frame for affinity taxa filtering for temperature cutoff and 1
#   sd from the mean:
df.affinity <- subset(df, Experiment == 'affinity' &
                        Temp.cutoff %in% c('low thermo greater than 50 C','mid thermo greater than 50 C')) %>%
  subset(mu > (mean(mu)-1*sd(mu))) %>%
  mutate(affinity.L2FC = L2FC)%>%
  dplyr::group_by(OTU) %>%
  dplyr::mutate(max.mu = max(mu)) %>%
  subset(mu == max.mu) %>%
  subset(select = c(OTU, affinity.L2FC)) %>%
  unique()%>%
  mutate(affinity = 'yes')

@@

x.1 <- df.full %>%
  subset(Experiment == 'survival') %>%
  subset(select = c(OTU, mu, Experiment,horizon,
                    fold.change, L2FC)) %>%
  dplyr::group_by(OTU, Experiment) %>%
  dplyr::mutate(max.mu = max(abs(mu))) %>%
  subset(max.mu == abs(mu)) %>%
  dplyr::mutate(survival.L2FC = L2FC) %>%
  subset(select = c(OTU, survival.L2FC)) %>%
  unique()

x.2 <- df.full %>%
  subset(Experiment == 'fast growth') %>%
  subset(select = c(OTU, mu, Experiment,horizon,
                    fold.change, L2FC)) %>%
  dplyr::group_by(OTU, Experiment) %>%
  dplyr::mutate(max.mu = max(abs(mu))) %>%
  subset(max.mu == abs(mu)) %>%
  dplyr::mutate(fast.L2FC = L2FC) %>%
  subset(select = c(OTU, fast.L2FC)) %>%
  unique()

x.3 <- df.full %>%
  subset(Experiment == 'affinity') %>%
  subset(select = c(OTU, mu, Experiment,horizon,
                    fold.change, L2FC)) %>%
  dplyr::group_by(OTU, Experiment) %>%
  dplyr::mutate(max.mu = max(abs(mu))) %>%
  subset(max.mu == abs(mu)) %>%
  dplyr::mutate(affinity.L2FC = L2FC) %>%
  subset(select = c(OTU, affinity.L2FC)) %>%
  unique()

@@

# Ordination plot with horizons and deg.hrs
p1 = plot_ordination(ps.norm.gDNA, MyNMDS.full.gDNA, axes = c(1,2), 
                      color = "burn.trtmt",
                      shape = 'incub.trtmt') + 
  facet_grid(~horizon, labeller = labeller(horizon = HorizonLabels,
                                                   DNA.type = DNALabels,
                                                   incub.trtmt = IncubLabels))+
  #facet_grid(~horizon, labeller = labeller(horizon = HorizonLabels))+
  geom_point(size=3, alpha=0.8) +
  #geom_line(aes(group = core.id.hor)) +
  labs(color = 'Burn treatment',
       #color = expression("Degree ("*degree*C*") hours"), 
       shape = 'Experiment') +
  #scale_color_gradientn(colours = c('gold2','red','red4','black')) +
  scale_color_manual(values = c('black','orange','red'),
                     labels = c('Unburned control', 'Wet soil burn','Wry soil burn'),
                     breaks = c('control','wet','dry'))+
  scale_shape_manual(values = c('circle','square','triangle'),
                     labels = c('Fire survival', 'Fast growth','Post-fire envir. affinity'),
                     breaks = c('pb','SI','LIwA')) +
  #scale_shape_discrete(labels = c('Picea' = 'Picea spp.', 'Populus_tremuloides' = 'Populus tremuloides','Pinus_banksiana' = 'Pinus banksiana')) +
  #scale_shape_manual(values = c('circle','triangle'),
   #                  labels = c('O horizon','Mineral'),
    #                 breaks = c('O','A')) + 
  theme(legend.text = element_text(face = 'italic',size = 16),
        axis.title = element_text(size=16),
        axis.text = element_text(size=16),
        legend.title = element_text(size=16)) + 
  theme_bw()

@@

unique(subset(df, select = c(Experiment, DNA.type, Comparison, pH.cutoff, Temp.cutoff)))

@@

df$horizon <- factor(df$horizon, levels = c('O','A'))
df$Experiment <- factor(df$Experiment, levels = c('survival','fast growth','affinity'))

for (i in 1:nrow(df)) {
  if (abs(df$Estimate[i]) > 2) {
    df$trimmed.Estimate[i] = df$Estimate[i]
  } else {
    df$trimmed.Estimate[i] = NA
  }
}

p = ggplot(df) + 
  geom_histogram(aes(Estimate),fill = 'red', binwidth=1) + 
  #geom_histogram(aes(trimmed.Estimate), fill = 'blue', binwidth=1) + 
  theme_bw() + 
  facet_grid(Experiment+DNA.type~horizon, scales = 'free')

length(unique(subset(df, Temp.cutoff == 'Low thermo greater than 50 C' &
                       Experiment == 'survival')$OTU))

p1 = ggplot(subset(df, Experiment == 'survival'), aes(Estimate)) +
  geom_histogram() + 
  theme_bw() + 
  facet_grid(horizon+Comparison~Temp.cutoff, scales = 'free')

p2 = ggplot(subset(df, Experiment == 'fast growth'), aes(Estimate)) +
  geom_histogram() + 
  theme_bw() + 
  facet_grid(horizon+Comparison~pH.cutoff, scales = 'free')

p3 = ggplot(subset(df, Experiment == 'survival'), aes(Estimate)) +
  geom_histogram() + 
  theme_bw() + 
  facet_grid(horizon+Comparison~Temp.cutoff, scales = 'free')

length(unique(subset(df, Estimate > 0 & Experiment == 'affinity')$OTU))
length(unique(subset(df, Estimate < 0 & Experiment == 'affinity')$OTU))
length(unique(subset(df, Estimate > 1 & Experiment == 'affinity')$OTU))
length(unique(subset(df, Estimate < -1 & Experiment == 'affinity')$OTU))

dim(subset(df, Experiment == 'fast growth' &
             horizon == 'O' &
             Comparison == 'pb.dry.v.SI.dry' &
             pH.cutoff != 'null'))
             #Temp.cutoff != 'null'))

@@

p1 = ggplot(subset(df.LI.responders, horizon == 'O' & site != 19), aes(x=cntl.pH, y=Abundance, fill=Response))+
  geom_bar(stat = 'identity') +
  facet_grid(incub.trtmt~burn.trtmt, scales = 'free', 
             labeller = labeller(incub.trtmt = IncubLabels, 
                                 horizon = HorizonLabels,
                                 burn.trtmt = BurnLabels)) +
  scale_fill_manual(values = c('forestgreen','grey50','red'),
                     limits = c('positive','none', 'negative'),
                     labels = c('Positive','No Response', 'Negative')) +
  labs(title = 'Experiment3: Both LIn and LIwA data: controlling for pre-burn pH',
       y = 'Relative abundance') + 
  theme(legend.position = 'bottom',
        axis.text.x = element_text(size=8), 
        legend.text = element_text(size=8))

@@

p2 = ggplot(subset(df.LI.sum, horizon == 'O' & Response != 'none' & burn.trtmt == 'dry'), aes(x=pH, y=(sum.abun), color = site))+
  geom_point(size=3) +
  facet_grid(incub.trtmt~burn.trtmt, scales = 'free', 
             labeller = labeller(incub.trtmt = IncubLabels, 
                                 horizon = HorizonLabels,
                                 burn.trtmt = BurnLabels)) +
        stat_smooth(method=lm,se = FALSE,color='black') +
  #scale_color_manual(values = c('forestgreen','grey50','red'),
   #                  limits = c('positive','none', 'negative'),
    #                 labels = c('Positive','No Response', 'Negative')) +
  labs(title = 'Experiment3: Responders identified LIwA.dry.vs.control \ncontrolling for pre-burn pH',
       y = 'Relative abundance',
       x = 'post-burn pH') + 
  theme(legend.position = 'bottom',
        axis.text.x = element_text(size=8), 
        legend.text = element_text(size=8))+
  ylim(0,0.2)

@@

p <- ggplot(data = subset(df, burn.trtmt == 'dry' & horizon == 'O'), 
            aes(x=site, y = Abundance, Fill = Experiment)) + 
  theme_bw()+
  #geom_point()+
  geom_bar(stat = 'identity') +
  facet_wrap(~Experiment, scale = 'free') + 
  #stat_smooth(method=lm,se = FALSE,color='black') +
  theme(axis.text.x = element_text(angle = 90))
```

@@

df.PB.pos.rspd <- subset(df.full, Experiment == 'survival' & Estimate > 0) %>%
  subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
                            'Mid thermo greater than 50 C')) %>%
  group_by(OTU,horizon) %>%
  mutate(max.Estimate = max(Estimate)) %>%
  subset(max.Estimate == Estimate) %>%  
  mutate(Response = 'positive') %>%
  unique()

df.PB.neg.rspd <- subset(df.full, Experiment == 'survival' & Estimate < 0) %>%
  subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
                            'Mid thermo greater than 50 C')) %>%
  group_by(OTU, horizon) %>%
  mutate(min.Estimate = min(Estimate)) %>%
  subset(min.Estimate == Estimate) %>%
  mutate(Response = 'negative') %>%
  unique()

@@

df.SI.cntl.pos.rspd <- subset(df.full, Experiment == 'fast growth' & Estimate > 0) %>%
  subset(Comparison == 'pb.control.v.SI.control') %>%
  group_by(OTU, horizon) %>%
  mutate(max.Estimate = max(Estimate)) %>%
  subset(max.Estimate == Estimate) %>%
  unique()
df.SI.cntl.neg.rspd <- subset(df.full, Experiment == 'fast growth' & Estimate < 0) %>%
  subset(Comparison == 'pb.control.v.SI.control') %>%
  group_by(OTU, horizon) %>%
  mutate(min.Estimate = min(Estimate)) %>%
  subset(min.Estimate == Estimate) %>%
  unique()

df.SI.pos.rspd <- subset(df.full, Experiment == 'fast growth' & Estimate > 0) %>%
  subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
                            'Mid thermo greater than 50 C')) %>%
  group_by(OTU, horizon) %>%
  mutate(max.Estimate = max(Estimate)) %>%
  subset(max.Estimate == Estimate) %>%
  mutate(Response = 'positive') %>%
  unique() %>% 
  subset(!(OTU %in% df.SI.cntl.pos.rspd$OTU))
length(unique(df.SI.pos.rspd$OTU))

df.SI.neg.rspd <- subset(df.full, Experiment == 'fast growth' & Estimate < 0) %>%
  subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
                            'Mid thermo greater than 50 C')) %>%
  group_by(OTU, horizon) %>%
  mutate(min.Estimate = min(Estimate)) %>%
  subset(min.Estimate == Estimate) %>%
  unique() %>%
  mutate(Response = 'negative') %>%
  subset(!(OTU %in% df.SI.cntl.neg.rspd$OTU))

@@

# LIwA:
df.LIwA <- subset(df.full, Experiment == 'affinity')

df.LIwA.pos.rspd <- subset(df.full, Experiment == 'affinity' & Estimate > 0) %>%
  subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
                            'Mid thermo greater than 50 C')) %>%
  group_by(OTU, horizon) %>%
  mutate(max.Estimate = max(Estimate)) %>%
  subset(max.Estimate == Estimate) %>%
  mutate(Response = 'positive') %>%
  unique() 
length(unique(df.LIwA.pos.rspd$OTU))

df.LIwA.neg.rspd <- subset(df.full, Experiment == 'affinity' & Estimate < 0) %>%
  subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
                            'Mid thermo greater than 50 C')) %>%
  group_by(OTU,horizon) %>%
  mutate(min.Estimate = min(Estimate)) %>%
  subset(min.Estimate == Estimate) %>%
  mutate(Response = 'negative') %>%
  unique() 
length(unique(df.LIwA.neg.rspd$OTU))

@@

p = ggplot(subset(df.responders, Phylum == 'Firmicutes'), aes(x=Estimate, y = Genus, color = Experiment)) + 
  geom_point(size=2) + 
  theme_bw() + 
  facet_grid(horizon~Experiment) + 
  geom_vline(xintercept = 0)

>>>>

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(out.width = '100%')

@@

df.fast <- subset(df.full, experiment == 'fast growth' &
                        Estimate > (mean(Estimate)-1*sd(Estimate))) %>%
  mutate(fast.est = Estimate)%>%
  dplyr::group_by(OTU) %>%
  dplyr::mutate(max.Estimate = max(Estimate)) %>%
  subset(Estimate == max.Estimate) %>%
  subset(select = c(OTU, Estimate, SE, t, p, p_fdr,Comparison, experiment,
                    horizon, Domain, Phylum, Class, Order, Family, Genus, 
                    Species, DNA.type, fast.est)) %>%
  unique()

@@

df.SI.responders <- df.full.OTU %>%
  subset(experiment == 'fast growth') %>%
  merge(RDP)

@@

# Figure 6: Trade offs
```{r}

df <- read.csv('../../data/sequence-data/LibCombined/corncob-output/Manuscript/all-responders.csv')
df.L2FC <- read.csv('../../data/sequence-data/LibCombined/corncob-output/Full_L2FC.csv')

# Checking to make sure that L2FC calculations didn't drop any OTUs. 
df.survival <- df %>%
  subset(experiment == 'survival'&
           T.cutoff %in% c('Low thermo > 50C','Mid thermo > 50C') & 
           intercept > 0) %>%
  subset(intercept > (mean(intercept)-1*sd(intercept)) ) %>% 
  subset(select = c(OTU,Phylum, Class, Order, Family, Genus, Species)) %>%
  unique()

df.survival.L2FC <- df.L2FC %>%
  subset(experiment == 'survival'  &
           T.cutoff %in% c('low thermo > 50C','Mid thermo > 50C') &
           mu > 0) %>%
  subset(mu > (mean(mu)-1*sd(mu))) %>%
  subset(select = c(OTU)) %>%
  unique()

@@

df.fast <- df %>%
  subset(experiment == 'fast growth'&
           intercept > 0) %>%
  subset(intercept > (mean(intercept)-1*sd(intercept)) ) %>% 
  subset(select = c(OTU,Phylum, Class, Order, Family, Genus, Species)) %>%
  unique()
dim(df.fast)

df.fast.L2FC  <- df.L2FC %>%
  subset(experiment == 'fast growth'  &
           mu > 0) %>%
  subset(mu > (mean(mu)-1*sd(mu))) %>%
  subset(select = c(OTU)) %>%
  unique() 
dim(df.fast.L2FC)
df.fast.merge <- merge(df.fast.L2FC, df.fast)

df.affinity <- df %>%
  subset(experiment == 'affinity'&
           T.cutoff %in% c('Low thermo > 50','Mid thermo > 50') &
           intercept > 0) %>%
  subset(intercept > (mean(intercept)-1*sd(intercept)) ) %>% 
  subset(select = c(OTU,Phylum, Class, Order, Family, Genus, Species)) %>%
  unique()
dim(df.affinity)

df.affinity.L2FC  <- df.L2FC %>%
  subset(experiment == 'affinity'  &
           T.cutoff %in% c('low thermo > 50 C','mid thermo > 50 C') &
           mu > 0) %>%
  subset(mu > (mean(mu)-1*sd(mu))) %>%
  subset(select = c(OTU)) %>%
  unique() 
dim(df.affinity.L2FC)

@@

# Create a dataframe for survivors filtering by temperature cutof and 1 sd from 
#   the mean of the intercept. Remove duplicate taxa. 
df.survival <- subset(df, experiment == 'survival' &
                        T.cutoff %in% c('low thermo > 50 C','mid thermo > 50 C')) %>%
  subset(mu > (mean(mu)-1*sd(mu))) %>%
  mutate(survival.L2FC = L2FC) %>%
  dplyr::group_by(OTU) %>%
  dplyr::mutate(max.mu = max(mu)) %>%
  subset(mu == max.mu) %>%
  subset(select = c(OTU, survival.L2FC)) %>%
  unique()%>%
  mutate(survivor = 'yes')

# Create dataframe for fast growers filtering for 1 sd from the mean: -----
df.fast <- subset(df, experiment == 'fast growth') %>%
  subset(mu > (mean(mu)-1*sd(mu))) %>%
  mutate(fast.L2FC = L2FC)%>%
  dplyr::group_by(OTU) %>%
  dplyr::mutate(max.mu = max(mu)) %>%
  subset(mu == max.mu) %>%
  subset(select = c(OTU, fast.L2FC)) %>%
  unique() %>%
  mutate(fast = 'yes')

# Create data frame for affinity taxa filtering for temperature cutoff and 1
#   sd from the mean:
df.affinity <- subset(df, experiment == 'affinity' &
                        T.cutoff %in% c('Low thermo > 50C','Mid thermo > 50C')) %>%
  subset(mu > (mean(mu)-1*sd(mu))) %>%
  mutate(affinity.L2FC = L2FC)%>%
  dplyr::group_by(OTU) %>%
  dplyr::mutate(max.mu = max(mu)) %>%
  subset(mu == max.mu) %>%
  subset(select = c(OTU, affinity.L2FC)) %>%
  unique()%>%
  mutate(affinity = 'yes')

@@

x.1 <- df.full %>%
  subset(experiment == 'survival') %>%
  subset(select = c(OTU, mu, experiment,horizon,
                    fold.change, L2FC)) %>%
  dplyr::group_by(OTU, experiment) %>%
  dplyr::mutate(max.mu = max(abs(mu))) %>%
  subset(max.mu == abs(mu)) %>%
  dplyr::mutate(survival.L2FC = L2FC) %>%
  subset(select = c(OTU, survival.L2FC)) %>%
  unique()

x.2 <- df.full %>%
  subset(experiment == 'fast growth') %>%
  subset(select = c(OTU, mu, experiment,horizon,
                    fold.change, L2FC)) %>%
  dplyr::group_by(OTU, experiment) %>%
  dplyr::mutate(max.mu = max(abs(mu))) %>%
  subset(max.mu == abs(mu)) %>%
  dplyr::mutate(fast.L2FC = L2FC) %>%
  subset(select = c(OTU, fast.L2FC)) %>%
  unique()

x.3 <- df.full %>%
  subset(experiment == 'affinity') %>%
  subset(select = c(OTU, mu, experiment,horizon,
                    fold.change, L2FC)) %>%
  dplyr::group_by(OTU, experiment) %>%
  dplyr::mutate(max.mu = max(abs(mu))) %>%
  subset(max.mu == abs(mu)) %>%
  dplyr::mutate(affinity.L2FC = L2FC) %>%
  subset(select = c(OTU, affinity.L2FC)) %>%
  unique()

@@

# Ordination plot with horizons and deg.hrs
p1 = plot_ordination(ps.norm.gDNA, MyNMDS.full.gDNA, axes = c(1,2), 
                      color = "burn.trtmt",
                      shape = 'incub.trtmt') + 
  facet_grid(~horizon, labeller = labeller(horizon = HorizonLabels,
                                                   DNA.type = DNALabels,
                                                   incub.trtmt = IncubLabels))+
  #facet_grid(~horizon, labeller = labeller(horizon = HorizonLabels))+
  geom_point(size=3, alpha=0.8) +
  #geom_line(aes(group = core.id.hor)) +
  labs(color = 'Burn treatment',
       #color = expression("Degree ("*degree*C*") hours"), 
       shape = 'experiment') +
  #scale_color_gradientn(colours = c('gold2','red','red4','black')) +
  scale_color_manual(values = c('black','orange','red'),
                     labels = c('Unburned control', 'Wet soil burn','Wry soil burn'),
                     breaks = c('control','wet','dry'))+
  scale_shape_manual(values = c('circle','square','triangle'),
                     labels = c('Fire survival', 'Fast growth','Post-fire envir. affinity'),
                     breaks = c('pb','SI','LIwA')) +
  #scale_shape_discrete(labels = c('Picea' = 'Picea spp.', 'Populus_tremuloides' = 'Populus tremuloides','Pinus_banksiana' = 'Pinus banksiana')) +
  #scale_shape_manual(values = c('circle','triangle'),
   #                  labels = c('O horizon','Mineral'),
    #                 breaks = c('O','A')) + 
  theme(legend.text = element_text(face = 'italic',size = 16),
        axis.title = element_text(size=16),
        axis.text = element_text(size=16),
        legend.title = element_text(size=16)) + 
  theme_bw()

@@

unique(subset(df, select = c(experiment, DNA.type, Comparison, pH.cutoff, Temp.cutoff)))

@@

df$horizon <- factor(df$horizon, levels = c('O','A'))
df$experiment <- factor(df$experiment, levels = c('survival','fast growth','affinity'))

for (i in 1:nrow(df)) {
  if (abs(df$intercept[i]) > 2) {
    df$trimmed.intercept[i] = df$intercept[i]
  } else {
    df$trimmed.intercept[i] = NA
  }
}

p = ggplot(df) + 
  geom_histogram(aes(intercept),fill = 'red', binwidth=1) + 
  #geom_histogram(aes(trimmed.intercept), fill = 'blue', binwidth=1) + 
  theme_bw() + 
  facet_grid(experiment+DNA.type~horizon, scales = 'free')

length(unique(subset(df, Temp.cutoff == 'Low thermo greater than 50 C' &
                       experiment == 'survival')$OTU))

p1 = ggplot(subset(df, experiment == 'survival'), aes(intercept)) +
  geom_histogram() + 
  theme_bw() + 
  facet_grid(horizon+Comparison~Temp.cutoff, scales = 'free')

p2 = ggplot(subset(df, experiment == 'fast growth'), aes(intercept)) +
  geom_histogram() + 
  theme_bw() + 
  facet_grid(horizon+Comparison~pH.cutoff, scales = 'free')

p3 = ggplot(subset(df, experiment == 'survival'), aes(intercept)) +
  geom_histogram() + 
  theme_bw() + 
  facet_grid(horizon+Comparison~Temp.cutoff, scales = 'free')

length(unique(subset(df, intercept > 0 & experiment == 'affinity')$OTU))
length(unique(subset(df, intercept < 0 & experiment == 'affinity')$OTU))
length(unique(subset(df, intercept > 1 & experiment == 'affinity')$OTU))
length(unique(subset(df, intercept < -1 & experiment == 'affinity')$OTU))

dim(subset(df, experiment == 'fast growth' &
             horizon == 'O' &
             Comparison == 'pb.dry.v.SI.dry' &
             pH.cutoff != 'null'))
             #Temp.cutoff != 'null'))

@@

p1 = ggplot(subset(df.LI.responders, horizon == 'O' & site != 19), aes(x=cntl.pH, y=Abundance, fill=Response))+
  geom_bar(stat = 'identity') +
  facet_grid(incub.trtmt~burn.trtmt, scales = 'free', 
             labeller = labeller(incub.trtmt = IncubLabels, 
                                 horizon = HorizonLabels,
                                 burn.trtmt = BurnLabels)) +
  scale_fill_manual(values = c('forestgreen','grey50','red'),
                     limits = c('positive','none', 'negative'),
                     labels = c('Positive','No Response', 'Negative')) +
  labs(title = 'experiment3: Both LIn and LIwA data: controlling for pre-burn pH',
       y = 'Relative abundance') + 
  theme(legend.position = 'bottom',
        axis.text.x = element_text(size=8), 
        legend.text = element_text(size=8))

@@

p2 = ggplot(subset(df.LI.sum, horizon == 'O' & Response != 'none' & burn.trtmt == 'dry'), aes(x=pH, y=(sum.abun), color = site))+
  geom_point(size=3) +
  facet_grid(incub.trtmt~burn.trtmt, scales = 'free', 
             labeller = labeller(incub.trtmt = IncubLabels, 
                                 horizon = HorizonLabels,
                                 burn.trtmt = BurnLabels)) +
        stat_smooth(method=lm,se = FALSE,color='black') +
  #scale_color_manual(values = c('forestgreen','grey50','red'),
   #                  limits = c('positive','none', 'negative'),
    #                 labels = c('Positive','No Response', 'Negative')) +
  labs(title = 'experiment3: Responders identified LIwA.dry.vs.control \ncontrolling for pre-burn pH',
       y = 'Relative abundance',
       x = 'post-burn pH') + 
  theme(legend.position = 'bottom',
        axis.text.x = element_text(size=8), 
        legend.text = element_text(size=8))+
  ylim(0,0.2)

@@

p <- ggplot(data = subset(df, burn.trtmt == 'dry' & horizon == 'O'), 
            aes(x=site, y = Abundance, Fill = experiment)) + 
  theme_bw()+
  #geom_point()+
  geom_bar(stat = 'identity') +
  facet_wrap(~experiment, scale = 'free') + 
  #stat_smooth(method=lm,se = FALSE,color='black') +
  theme(axis.text.x = element_text(angle = 90))
```

@@

df.PB.pos.rspd <- subset(df.full, experiment == 'survival' & Estimate > 0) %>%
  subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
                            'Mid thermo greater than 50 C')) %>%
  group_by(OTU,horizon) %>%
  mutate(max.Estimate = max(Estimate)) %>%
  subset(max.Estimate == Estimate) %>%  
  mutate(Response = 'positive') %>%
  unique()

df.PB.neg.rspd <- subset(df.full, experiment == 'survival' & Estimate < 0) %>%
  subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
                            'Mid thermo greater than 50 C')) %>%
  group_by(OTU, horizon) %>%
  mutate(min.Estimate = min(Estimate)) %>%
  subset(min.Estimate == Estimate) %>%
  mutate(Response = 'negative') %>%
  unique()

@@

df.SI.cntl.pos.rspd <- subset(df.full, experiment == 'fast growth' & Estimate > 0) %>%
  subset(Comparison == 'pb.control.v.SI.control') %>%
  group_by(OTU, horizon) %>%
  mutate(max.Estimate = max(Estimate)) %>%
  subset(max.Estimate == Estimate) %>%
  unique()
df.SI.cntl.neg.rspd <- subset(df.full, experiment == 'fast growth' & Estimate < 0) %>%
  subset(Comparison == 'pb.control.v.SI.control') %>%
  group_by(OTU, horizon) %>%
  mutate(min.Estimate = min(Estimate)) %>%
  subset(min.Estimate == Estimate) %>%
  unique()

df.SI.pos.rspd <- subset(df.full, experiment == 'fast growth' & Estimate > 0) %>%
  subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
                            'Mid thermo greater than 50 C')) %>%
  group_by(OTU, horizon) %>%
  mutate(max.Estimate = max(Estimate)) %>%
  subset(max.Estimate == Estimate) %>%
  mutate(Response = 'positive') %>%
  unique() %>% 
  subset(!(OTU %in% df.SI.cntl.pos.rspd$OTU))
length(unique(df.SI.pos.rspd$OTU))

df.SI.neg.rspd <- subset(df.full, experiment == 'fast growth' & Estimate < 0) %>%
  subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
                            'Mid thermo greater than 50 C')) %>%
  group_by(OTU, horizon) %>%
  mutate(min.Estimate = min(Estimate)) %>%
  subset(min.Estimate == Estimate) %>%
  unique() %>%
  mutate(Response = 'negative') %>%
  subset(!(OTU %in% df.SI.cntl.neg.rspd$OTU))

@@

# LIwA:
df.LIwA <- subset(df.full, experiment == 'affinity')

df.LIwA.pos.rspd <- subset(df.full, experiment == 'affinity' & Estimate > 0) %>%
  subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
                            'Mid thermo greater than 50 C')) %>%
  group_by(OTU, horizon) %>%
  mutate(max.Estimate = max(Estimate)) %>%
  subset(max.Estimate == Estimate) %>%
  mutate(Response = 'positive') %>%
  unique() 
length(unique(df.LIwA.pos.rspd$OTU))

df.LIwA.neg.rspd <- subset(df.full, experiment == 'affinity' & Estimate < 0) %>%
  subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
                            'Mid thermo greater than 50 C')) %>%
  group_by(OTU,horizon) %>%
  mutate(min.Estimate = min(Estimate)) %>%
  subset(min.Estimate == Estimate) %>%
  mutate(Response = 'negative') %>%
  unique() 
length(unique(df.LIwA.neg.rspd$OTU))

@@

p = ggplot(subset(df.responders, Phylum == 'Firmicutes'), aes(x=Estimate, y = Genus, color = experiment)) + 
  geom_point(size=2) + 
  theme_bw() + 
  facet_grid(horizon~experiment) + 
  geom_vline(xintercept = 0)
